Stack Safety as a Security Property

### 2020-06-29 main.tex
fix build

A trace over some type $A$ is a potentially infinite, nonempty
sequence of $A$s. We will mostly be concerned with sequences of
machines states, usually denoted $\machT$, and with sequences of
triples of (machine states, policy states, and observations), usually
denoted $\MPT$.
\rb{The way the definitions are set up, one may expect MPO, but\ldots}
To continue, we will require three \{four?} generic operations
on traces: a ``trace-of'' operation to construct the potentially
infinite traced induced by a step relation
\rb{not an op on traces per se?};
a ``split'', to break a
trace into two components based on a predicate; a ``join'', the
reverse of split; and a ``prefix'', as a shorthand to only keep the
first component of a split.

>>>>

A trace over some type $A$ is a potentially infinite, nonempty
sequence of $A$s. We will mostly be concerned with sequences of
machines states, usually denoted $\machT$, and with sequences of
triples of (machine states, policy states, and observations), usually
denoted $\MPT$.
\rb{The way the definitions are set up, one may expect MPO, but\ldots}
To continue, we will require three \rb{four?} generic operations
on traces: a ``trace-of'' operation to construct the potentially
infinite traced induced by a step relation
\rb{not an op on traces per se?};
a ``split'', to break a
trace into two components based on a predicate; a ``join'', the
reverse of split; and a ``prefix'', as a shorthand to only keep the
first component of a split.
